has mentored more than 3 postdoctoral research scientists, 8 doctoral and 4 master’s students, in addition to over 20 undergraduates and 1 high-school student from Illinois Tech, U Chicago, Stanford U, and the Illinois Mathematics and Science Academy. \SCTC and her collaborators have published articles, open-source mathematical software, and research blogs with the aforementioned PhD and MS students \cite{ChoEtal22a,QMCPy2020a,QMCBlog,
ChoEtal20a,WCCR18,ChoEtal17a} as well as undergraduates \cite{QMCPy2020a,QMCBlog,PCLD21,ZLWC21}. Being the first in her lower- and working-class family in Hong Kong to attend college, \SCTC relates particularly well with students from less privileged backgrounds. \SCTC has been a research faculty member at with Illinois Tech since 2013. She is currently the Chief Data Scientist at the Kamakura Corporation, a multinational company that specializes in financial risk-management software.  She was a co-recipient of the international research award, \SIAM Activity Group on Linear Algebra (SIAG/LA) Prize in 2012 and  a winner of the Top 100 Data \& Analytics Professional Award by OnConferences in 2021. 

\iffalse
has served as a research (co-)advisor or mentor to more than 3 postdoctoral research scientists, 8 doctoral and 4 master’s students, in addition to over 20 undergraduates and 1 high-school student from Illinois Tech, U Chicago, Stanford U, and the Illinois Mathematics and Science Academy. Most of the undergraduates she guided were visiting Illinois Tech from the UIUC as well as various universities from Brazil and China through Illinois Tech's research seminar courses, Summer research programs, and internship programs.  \SCTC and her collaborators have published peer-reviewed articles, open-source mathematical software, and research blogs with the aforementioned PhD and MS students \cite{ChoEtal22a,QMCPy2020a,QMCBlog,
ChoEtal20a,WCCR18,ChoEtal17a} as well as undergraduates \cite{QMCPy2020a,QMCBlog,PCLD21,ZLWC21}. At least 12 of the undergraduates she mentored applied to graduate schools with her recommendation letters; more than 6 received admissions into graduate programs in applied mathematics, statistics, computer science, or data science in NYU, Columbia U, Carnegie Mellon U,  Georgia Tech, UC San Diego, the University of Colorado Boulder, and Northeastern U. The high school student she guided in 2016 is a double major in mathematics and computer science at Harvey Mudd College. Aleksei Sorokin, an undergraduate at Illinois Tech she advised since he was a freshman taking her 2018 Summer course, \emph{Reliable Mathematical Software}, is now a first-year PhD student at Illinois Tech and an active researcher; see~\cite{sorokinnews}. Being the first in her lower- and working-class family in Hong Kong to attend college, \SCTC relates particularly well with students from less privileged backgrounds. Her research interests include designing  effective and efficient mathematical algorithms, applications of machine learning to big data in investment science, corporate finance, or social sciences. \SCTC has been an adjunct faculty with Illinois Tech since 2013. She is currently \href{https://seekingalpha.com/instablog/420043-donald-van-deventer/5424649-kamakura-names-dr-sou-cheng-t-choi-chief-data-scientist}{the Chief Data Scientist} at  \href{http://www.kamakuraco.com}{the Kamakura Corporation}, a multinational company that specializes in financial risk-management software, which implements the groundbreaking theories of Prof.~Robert A.~Jarrow, Cornell University~\cite{CJMP21,CJMP21b}, following the statistical advice of Prof.~Xiao-Li Meng at Harvard University. She was a co-recipient of the international research award, SIAM Activity Group on Linear Algebra (SIAG/LA) Prize in 2012 and  a winner of the Top 100 Data \& Analytics Professional Award by \href{https://www.onconferences.com/2021-data-analytics-winners}{OnConferences} in 2021. 

\fi

